Artin Group Presentations Arising from Cluster Algebras

### 2015-08-20 Paper.tex
changed satifying to satisfying

   \end{tikzpicture}
   \end{center}

\caption{Mutation of $\Gamma$ at a node k}\label{mutation}
\end{figure}

@@

\begin{lem} \label{Sym-Lem}
Let $\Gamma$ be a diagram of finite type which contains a chordless cycle C:
\begin{equation*}
\begin{tikzcd}
i_0 \arrow{r} & i_1 \arrow{r} & \cdots \arrow{r} & i_{d-1} \arrow{r} & i_0
\end{tikzcd}
\end{equation*}
so that all edges have weight 1. Then if W is a group generated by $s_{1}, \dots, s_{n}$ satifying the relations (T2) and $t(i_{a}, i_{a+1}) = e$ for some a $\in \{1, \dots, d\}$, all of the relations in (T3) hold for C.
\end{lem}

@@

\begin{thebibliography}{9}
\bibitem{BM13}
Michael Barot and Robert J. Marsh,
``Reflection Group Presentations Arising from Cluster Algebras,''
arXiv: 1112.2300v2, 2013

\bibitem{C06}
Ruth Charney,
``An Introduction to Right-Angled Artin Groups,''
arXiv:math/0610668, 2006

\bibitem{FT13}
A. Felikson and P. Tumarkin,
``Coxeter groups and their quotients arising from cluster algebras,''
arXiv:1307.0672v2, 2013

\bibitem{FZ02}
Sergey Fomin and Andrei Zelevinsky,
``Cluster Algebras I: Foundations,''
\textit{J. Amer. Math. Soc.}, 15, 497-529, 2002

\bibitem{FZ03}
Sergey Fomin and Andrei Zelevinsky,
``Cluster Algebras II: Finite type classification,''
\textit{Invent. Math.}, 154, 63-121, 2003

\bibitem{FN61}
R. Fox and L. Neuwirth,
``The Braid Groups,''
\textit{Mathematica Scandinavica}, 119-126, 1961

\bibitem{GM14}
Joseph Grant and Robert J. Marsh
``Braid groups and quiver mutation,''
arXiv:1408.5267, 2014

\bibitem{Q14}
Y. Qiu,
``On the spherical twists on 3-Calabi-Yau categories from marked surfaces,''
arXiv:1407.0806, 2014

>>>>

\end{tikzpicture}
\end{center}
\caption{Mutation of $\Gamma$ at a node k}\label{mutation}
\end{figure}

@@

\begin{lem} \label{Sym-Lem}
Let $\Gamma$ be a diagram of finite type which contains a chordless cycle C:
\begin{equation*}
\begin{tikzcd}
i_0 \arrow{r} & i_1 \arrow{r} & \cdots \arrow{r} & i_{d-1} \arrow{r} & i_0
\end{tikzcd}
\end{equation*}
so that all edges have weight 1. Then if W is a group generated by $s_{1}, \dots, s_{n}$ satisfying the relations (T2) and $t(i_{a}, i_{a+1}) = e$ for some a $\in \{1, \dots, d\}$, all of the relations in (T3) hold for C.
\end{lem}

@@

\begin{thebibliography}{Cha06}

\bibitem[BM13]{BM13}
Michael Barot and Robert~J. Marsh.
\newblock Reflection group presentations arising from cluster algebras.
\newblock arXiv: 1112.2300v2, 2013.

\bibitem[Cha06]{C06}
Ruth Charney.
\newblock An introduction to right-angled artin groups.
\newblock arXiv:math/0610668, 2006.

\bibitem[FN61]{FN61}
R.~Fox and L.~Neuwirth.
\newblock The braid groups.
\newblock {\em Mathematica Scandinavica}, pages 119--126, 1961.

\bibitem[FT13]{FT13}
A.~Felikson and P.~Tumarkin.
\newblock Coxeter groups and their quotients arising from cluster algebras.
\newblock arXiv:1307.0672v2, 2013.

\bibitem[FZ02]{FZ02}
Sergey Fomin and Andrei Zelevinsky.
\newblock Cluster algebras I: Foundations.
\newblock {\em J. Amer. Math. Soc.}, 15:497--529, 2002.

\bibitem[FZ03]{FZ03}
Sergey Fomin and Andrei Zelevinsky.
\newblock Cluster algebras II: Finite type classification.
\newblock {\em Invent. Math.}, 154:63--121, 2003.

\bibitem[GM14]{GM14}
Joseph Grant and Robert~J. Marsh.
\newblock Braid groups and quiver mutation.
\newblock arXiv:1408.5267, 2014.

\bibitem[Qiu14]{Q14}
Y.~Qiu.
\newblock On the spherical twists on 3-calabi-yau categories from marked
  surfaces.
\newblock arXiv:1407.0806, 2014.
